---
title: "Draft and FA Report"
subtitle: "2022 Season"
format:
  html:
      df-print: kable
      theme: cosmo
      self-contained: true
      toc: true
      fig-width: 8
      fig-height: 6
editor: visual
---

```{r}
#| label: load-packages-and-data
#| include: false
#| echo: false

library(tidyverse)
`%notin%` <- Negate(`%in%`)

draft_recap <- read_csv("../../../Data/CSV-files/draft_recap_2022.csv")
combined_stats_table <- read_rds("../../../Data/RDS-files/combined_stats_table_2022.rds")
combined_stats_table_2021 <- read_rds("../../../Data/RDS-files/combined_stats_table_2021.rds")
```

```{r}
#| label: data-setup
#| include: false
#| echo: false


top_defenders <-
  combined_stats_table %>%
  filter(fantasy_defender_status) %>%
  filter(!fantasy_forward_status) %>%
  filter(TOG > 50) %>%
  filter(games_played >= 5) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  head(48) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1]) %>%
  mutate(across(where(is.numeric), ~round(., 2)))

top_midfielders <-
  combined_stats_table %>%
  filter(fantasy_midfield_status) %>%
  filter(!fantasy_forward_status) %>%
  filter(!fantasy_defender_status) %>%
  filter(!fantasy_ruck_status) %>%
  filter(TOG > 50) %>%
  filter(games_played >= 5) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  head(64) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1]) %>%
  mutate(across(where(is.numeric), ~round(., 2)))

top_rucks <-
  combined_stats_table %>%
  filter(fantasy_ruck_status) %>%
  filter(!fantasy_forward_status) %>%
  filter(!fantasy_defender_status) %>%
  filter(TOG > 50) %>%
  filter(games_played >= 5) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  head(16) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1]) %>%
  mutate(across(where(is.numeric), ~round(., 2)))

top_forwards <-
  combined_stats_table %>%
  filter(fantasy_forward_status) %>%
  filter(TOG > 50) %>%
  filter(games_played >= 5) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  head(48) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1]) %>%
  mutate(across(where(is.numeric), ~round(., 2)))

all_player_rankings <-
  bind_rows(top_defenders, top_midfielders, top_rucks, top_forwards) %>%
  group_by(player_name) %>%
  filter(z_score == max(z_score)) %>%
  ungroup() %>%
  arrange(desc(z_score)) %>%
  mutate(ranking = row_number()) %>%
  relocate(ranking, .after = player_name) %>%
  mutate(across(where(is.numeric), ~round(., 2)))
```

```{r}
#| echo: false
#| include: false

best_draft_picks <-
  all_player_rankings %>%
  left_join(draft_recap) %>%
  filter(!is.na(pick)) %>%
  mutate(difference = pick - ranking) %>%
  arrange(desc(difference))

best_FA_pickups <-
  all_player_rankings %>%
  filter(player_name %notin% draft_recap$player_name)

```

```{r}
#| echo: false
#| include: false

worst_draft_picks <-
combined_stats_table %>%
  filter(player_name %in% draft_recap$player_name)

# Defender
top_defenders_worst <-
  worst_draft_picks %>%
  filter(fantasy_defender_status) %>%
  filter(!fantasy_forward_status) %>%
  filter(TOG > 50) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1])

# Midfield
top_midfielders_worst <-
  worst_draft_picks %>%
  filter(fantasy_midfield_status) %>%
  filter(!fantasy_forward_status) %>%
  filter(!fantasy_defender_status) %>%
  filter(!fantasy_ruck_status) %>%
  filter(TOG > 50) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1])
# Ruck
top_rucks_worst <-
  worst_draft_picks %>%
  filter(fantasy_ruck_status) %>%
  filter(!fantasy_forward_status) %>%
  filter(!fantasy_defender_status) %>%
  filter(TOG > 50) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1])

# Forward
top_forwards_worst <-
  worst_draft_picks %>%
  filter(fantasy_forward_status) %>%
  filter(TOG > 50) %>%
  group_by(player_name) %>%
  summarise(avg_score = mean(fantasy_points, na.rm = TRUE), games_played = max(games_played)) %>%
  arrange(desc(avg_score)) %>%
  ungroup() %>%
  mutate(mean_position_score = mean(avg_score),
         z_score = scale(avg_score)[,1])

# Combine into 1 to get redraft ranking
all_player_rankings_worst <-
  bind_rows(top_defenders_worst, top_midfielders_worst, top_rucks_worst, top_forwards_worst) %>%
  group_by(player_name) %>%
  filter(z_score == max(z_score)) %>%
  ungroup() %>%
  arrange(desc(z_score)) %>%
  mutate(ranking = row_number())

# Get actual draft position
worst_draft_picks <-
  all_player_rankings_worst %>%
  left_join(draft_recap) %>%
  mutate(difference = pick - ranking) %>%
  arrange(difference) %>%
  mutate(avg_score = round(avg_score, 2),
         z_score = round(z_score, 2))

```

```{r}
#| echo: false
#| include: false

# Create draft round variable
rounds <-
  c(
    rep(1, 8),
    rep(2, 8),
    rep(3, 8),
    rep(4, 8),
    rep(5, 8),
    rep(6, 8),
    rep(7, 8),
    rep(8, 8),
    rep(9, 8),
    rep(10, 8),
    rep(11, 8),
    rep(12, 8),
    rep(13, 8),
    rep(14, 8),
    rep(15, 8),
    rep(16, 8),
    rep(17, 8),
    rep(18, 8),
    rep(19, 8),
    rep(20, 8),
    rep(21, 8),
    rep(22, 8)
  )

draft_recap <-
  draft_recap %>%
  mutate(round = rounds)

# Get best draft pick by round
best_pick_by_round <-
  draft_recap %>%
  left_join(all_player_rankings %>% select(player_name, ranking)) %>%
  group_by(round) %>%
  filter(ranking == min(ranking, na.rm = TRUE))

# Get worst draft pick by round
worst_pick_by_round <-
  draft_recap %>%
  left_join(all_player_rankings_worst %>% select(player_name, ranking)) %>%
  group_by(round) %>%
  filter(ranking == max(ranking, na.rm = TRUE))

```

## 10 Best Draft Picks

```{r}
#| echo: false

best_draft_picks %>%
  select(
    Player = player_name,
    Team = team,
    Avg = avg_score,
    `Z-Score` = z_score,
    Games = games_played,
    Pick = pick,
    Rank = ranking,
    Diff = difference
  ) %>%
  head(10)

```

## Best Draft Picks By Round

```{r}
#| echo: false

best_pick_by_round %>%
  select(
    Round = round,
    Player = player_name,
    Team = team,
    Pick = pick,
    Rank = ranking
  )

```

## 10 Best FA Pickups

```{r}
#| echo: false

best_FA_pickups %>%
  filter(player_name != "Oscar McInerney") %>%
  select(
    Player = player_name,
    Avg = avg_score,
    `Z-Score` = z_score,
    Games = games_played,
    Rank = ranking
  ) %>%
  head(10)

```

## 10 Worst Draft Picks

```{r}
#| echo: false

worst_draft_picks %>%
  select(
    Player = player_name,
    Team = team,
    Avg = avg_score,
    `Z-Score` = z_score,
    Games = games_played,
    Pick = pick,
    Rank = ranking,
    Diff = difference
  ) %>%
  head(10)

```

## Worst Draft Picks By Round

```{r}
#| echo: false

worst_pick_by_round %>%
  select(
    Round = round,
    Player = player_name,
    Team = team,
    Pick = pick,
    Rank = ranking
  )

```

## Biggest Changes in Average Compared to 2021 Season

##### Min 5 games played in both seasons, injury affected scores (<50 % TOG) excluded

```{r}
#| include: false

avgs_2022 <- 
combined_stats_table %>%
filter(TOG > 50) %>%
filter(games_played >= 5) %>%
  summarise(avg_score_2022 = mean(fantasy_points, na.rm = TRUE)) %>%
  arrange(desc(avg_score_2022))
  
avgs_2021 <- 
combined_stats_table_2021 %>%
filter(TOG > 50) %>%
filter(games_played >= 5) %>%
  summarise(avg_score_2021 = mean(fantasy_points, na.rm = TRUE)) %>%
  arrange(desc(avg_score_2021))

comparison <-
  full_join(avgs_2022, avgs_2021) %>%
  mutate(difference = avg_score_2022 - avg_score_2021)

```

::: panel-tabset
## Improved

```{r}
#| echo: false
#| warning: false
#| message: false

comparison %>%
  left_join(draft_recap) %>%
  filter(!is.na(pick)) %>%
  arrange(desc(difference)) %>%
  transmute(Player = player_name,
            Pick = pick,
            Team = team,
         `2022 Avg` = round(avg_score_2022, 2),
         `2021 Avg` = round(avg_score_2021, 2),
         Diff = round(difference, 2)) %>%
  head(20)
```

## Regressed

```{r}
#| echo: false
#| warning: false
#| message: false

comparison %>%
  left_join(draft_recap) %>%
  filter(!is.na(pick)) %>%
  arrange(difference) %>%
  transmute(Player = player_name,
            Pick = pick,
            Team = team,
         `2022 Avg` = round(avg_score_2022, 2),
         `2021 Avg` = round(avg_score_2021, 2),
         Diff = round(difference, 2)) %>%
  head(20)
```
:::
