---
title: "Player Summary"
subtitle: "2022 Season"
format:
  html:
      df-print: kable
      theme: cosmo
      self-contained: true
      toc: true
editor: visual
---

```{r}
#| label: load-packages-and-data
#| include: false

# Libraries, functions and data
library(tidyverse)
library(rvest)
combined_stats_table <- read_rds("Data/RDS-files/combined_stats_table_2022.rds")
player_details <- read_rds("Data/RDS-files/player_details.rds")
draft_recap <- read_csv("Data/CSV-files/draft_recap_2022.csv")
`%notin%` <- Negate(`%in%`)
```

```{r}
#| label: process-data
#| include: false

##%######################################################%##
#                                                          #
####             Read in HTML of team pages             ####
#                                                          #
##%######################################################%##

#===============================================================================
# Get list of files in Data/HTML-files folder
#===============================================================================

team_files <- dir("Data/HTML-files/teams")
team_files <- sort(team_files)

#===============================================================================
# Create function that reads html and outputs players table
#===============================================================================

get_players <- function(html_path) {
  # Read HTML from path
  full_path <- paste("Data/HTML-files/teams/", html_path, sep = "")
  html_source <- read_html(full_path)
  
  # Create players vector and return
  players <-
    html_source %>%
    html_elements(".jfnohy") %>%
    html_text2()
  
  return(players)
}

#===============================================================================
# Create function that reads html and outputs teams table
#===============================================================================

get_teams <- function(html_path) {
  # Read HTML from path
  full_path <- paste("Data/HTML-files/teams/", html_path, sep = "")
  html_source <- read_html(full_path)
  
  # Create teams vector and return
  teams <-
    html_source %>%
    html_elements(".jfIbnL") %>%
    html_text2()
  
  return(teams)
}

#===============================================================================
# Map functions to list to get coaches and their players each round
#===============================================================================

all_players <- map(team_files, get_players)
all_teams <- map(team_files, get_teams)

# Get teams list in order they appear
all_teams_list <- all_teams[[1]]

# Get list of rounds
rounds <-
  c(
    "Round 1",
    "Round 2",
    "Round 3",
    "Round 4",
    "Round 5",
    "Round 6",
    "Round 7",
    "Round 8",
    "Round 9",
    "Round 10",
    "Round 11",
    "Round 15",
    "Round 16",
    "Round 17"
  )

##%######################################################%##
#                                                          #
####          Create function to extract each           ####
####          coaches fielded team each round           ####
#                                                          #
##%######################################################%##

# Create empty list of teams
all_fielded_teams <- list()

#===============================================================================
# Loop through and populate list of teams for each round
#===============================================================================

for (i in 1:length(rounds)){
  
  # Get tibble with player name
  fielded_team <- tibble(player_name = all_players[[i]], round_number = rounds[i])
  
  # Add team names
  fielded_team <-
    fielded_team %>%
    mutate(fantasy_team =
             case_when(
               row_number() <= 22 ~ all_teams_list[1],
               between(row_number(), 23, 44) ~ all_teams_list[2],
               between(row_number(), 45, 66) ~ all_teams_list[3],
               between(row_number(), 67, 88) ~ all_teams_list[4],
               between(row_number(), 89, 110) ~ all_teams_list[5],
               between(row_number(), 111, 132) ~ all_teams_list[6],
               between(row_number(), 133, 154) ~ all_teams_list[7],
               between(row_number(), 155, 176) ~ all_teams_list[8]
               )
           )
  
  # Remove positions and new line from player_name variable
  fielded_team$player_name <- str_remove_all(fielded_team$player_name, "\\n.*$")
  
  # Created fielded position variable
  fielded_team <-
    fielded_team %>%
    group_by(fantasy_team) %>%
    mutate(
      fielded_position =
        case_when(
          row_number() <= 5 ~ "Defender",
          between(row_number(), 6, 12) ~ "Midfielder",
          row_number() == 13 ~ "Ruck",
          between(row_number(), 14, 18) ~ "Forward",
          between(row_number(), 19, 22) ~ "Interchange"
        )
    )
  
  # Push to list
  all_fielded_teams[[i]] <- fielded_team
}

#===============================================================================
# Collapse list into a single dataframe for analysis
#===============================================================================

all_fielded_teams <- bind_rows(all_fielded_teams)

##%######################################################%##
#                                                          #
####   Combine fielded teams list with combined stats   ####
####          table to get scores and TOG data          ####
#                                                          #
##%######################################################%##

#===============================================================================
# Get filtered combined stats data
#===============================================================================
combined_stats_table_filtered <-
  combined_stats_table %>%
  mutate(
    player_first_initial = str_extract(player_name, "^[A-Z]"),
    player_middle_initial = str_extract(player_name, " [A-Z]\\. "),
    player_last_name = str_extract(player_name, "([A-Za-z-']*$)|(De Goey)|(De Koning)")
  ) %>%
  mutate(player_middle_initial = ifelse(is.na(player_middle_initial), "", player_middle_initial)) %>%
  mutate(player_middle_initial = str_remove_all(player_middle_initial, " ")) %>%
  mutate(
    player_name_initials = paste(
      player_first_initial,
      ". ",
      player_last_name,
      sep = ""
    )
  ) %>%
  transmute(
    player_name,
    player_name_initials,
    club = team,
    round_number = as.character(round_number),
    fantasy_points,
    TOG,
    dob,
    start_time,
    height,
    weight
  )

#===============================================================================
# Fix names for players that share first initial 
# and last name with others in competition
#===============================================================================

duplicate_names <- combined_stats_table_filtered %>%
  ungroup() %>%
  distinct(player_name_initials, club) %>%
  group_by(player_name_initials) %>%
  filter(max(row_number()) > 1) %>%
  arrange(player_name_initials) %>%
  filter(player_name_initials %in% all_fielded_teams$player_name)

#===============================================================================
# For both the all_fielded_teams and combined_stats_filtered_tables,
# if a player is a duplicate player, use their full name instead
#===============================================================================

# Get players fielded that have a duplicate
all_fielded_teams_duplicate_names <-
  all_fielded_teams %>%
  filter(player_name %in% duplicate_names$player_name_initials) %>%
  distinct(player_name, fantasy_team)

# Manually fix these in fielded teams table
all_fielded_teams <- 
  all_fielded_teams %>%
  ungroup() %>%
  mutate(player_name_2 =
           case_when(
             player_name == "J. Kelly" ~ "Josh Kelly",
             player_name == "B. Smith" & fantasy_team == "The Big 4 Bull" ~ "Bailey Smith",
             player_name == "B. Hill" ~ "Bradley Hill",
             player_name == "B. Smith" & fantasy_team == "BuIIs on parade" ~ "Brodie Smith",
             player_name == "A. Brayshaw" & fantasy_team == "Welcome To The Pig Sty" ~ "Andrew Brayshaw",
             player_name == "L. Jones" & fantasy_team == "the best team" ~ "Liam Jones",
             player_name == "L. Ryan" ~ "Luke Ryan",
             player_name == "L. McDonald" ~ "Luke McDonald",
             player_name == "D. Moore" ~ "Dylan Moore",
             player_name == "B. Ainsworth" ~ "Ben Ainsworth",
             player_name == "J. Kennedy" & fantasy_team == "BuIIs on parade" ~ "Josh P. Kennedy",
             player_name == "J. Kennedy" & fantasy_team == "The Big 4 Bull" ~ "Josh J. Kennedy",
             player_name == "A. Brayshaw" & fantasy_team == "DoYouLikeThat" ~ "Angus Brayshaw",
             player_name == "L. Young" ~ "Lachie Young"
           )
         ) %>%
  mutate(player_name = ifelse(!is.na(player_name_2), player_name_2, player_name)) %>%
  select(-player_name_2)

# Manually fix these in combined stats table
combined_stats_table_filtered <- 
  combined_stats_table_filtered %>%
  ungroup() %>%
  mutate(player_name_2 =
           case_when(
             player_name_initials == "J. Kelly" & club == "GWS Giants" ~ "Josh Kelly",
             player_name_initials == "B. Smith" & club == "Western Bulldogs" ~ "Bailey Smith",
             player_name_initials == "B. Hill" & club == "St Kilda" ~ "Bradley Hill",
             player_name_initials == "B. Smith" & club == "Adelaide Crows" ~ "Brodie Smith",
             player_name_initials == "A. Brayshaw" & club == "Fremantle" ~ "Andrew Brayshaw",
             player_name_initials == "L. Ryan" & club == "Fremantle" ~ "Luke Ryan",
             player_name_initials == "L. McDonald" & club == "North Melbourne" ~ "Luke McDonald",
             player_name_initials == "D. Moore" & club == "Hawthorn" ~ "Dylan Moore",
             player_name_initials == "B. Ainsworth" & club == "Gold Coast Suns" ~ "Ben Ainsworth",
             player_name_initials == "J. Kennedy" & club == "Sydney Swans" ~ "Josh P. Kennedy",
             player_name_initials == "J. Kennedy" & club == "West Coast Eagles" ~ "Josh J. Kennedy",
             player_name_initials == "A. Brayshaw" & club == "Melbourne" ~ "Angus Brayshaw",
             player_name_initials == "L. Young" & club == "North Melbourne" ~ "Lachie Young")) %>%
  mutate(player_name_initials = ifelse(!is.na(player_name_2), player_name_2, player_name_initials)) %>%
  select(-player_name_2) %>%
  rename(player_name_full = player_name)

#===============================================================================
# Join tables together
#===============================================================================

all_fielded_teams_full <-
  all_fielded_teams %>%
  left_join(combined_stats_table_filtered, by = c("player_name" = "player_name_initials", "round_number"))
  
#===============================================================================
# Add Emergency Status to get loopholed players / injury replacements
#===============================================================================

all_fielded_teams_full <-
  all_fielded_teams_full %>%
  mutate(fielded_position_2 =
           case_when(
             player_name_full == "Nick Daicos" & round_number == "Round 1" ~ "Emergency Midfielder",
             player_name_full == "Daniel Rioli" & round_number == "Round 1" ~ "Emergency Forward",
             player_name_full == "Kyle Langford" & round_number == "Round 1" ~ "Emergency Midfielder",
             player_name_full == "Nick Blakey" & round_number == "Round 1" ~ "Emergency Defender",
             player_name_full == "Dylan Shiel" & round_number == "Round 1" ~ "Emergency Midfielder",
             player_name_full == "Josh Battle" & round_number == "Round 1" ~ "Emergency Forward",
             
             player_name_full == "Brayden Fiorini" & round_number == "Round 2" ~ "Emergency Midfielder",
             player_name_full == "Jeremy Cameron" & round_number == "Round 2" ~ "Emergency Forward",
             player_name_full == "Hayden Crozier" & round_number == "Round 2" ~ "Emergency Defender",
             player_name_full == "Dayne Zorko" & round_number == "Round 2" ~ "Emergency Midfielder",
             player_name_full == "Aaron Naughton" & round_number == "Round 2" ~ "Emergency Forward",
             
             player_name_full == "Chad Warner" & round_number == "Round 3" ~ "Emergency Midfielder",
             player_name_full == "Dayne Zorko" & round_number == "Round 3" ~ "Emergency Midfielder",
             player_name_full == "Dylan Shiel" & round_number == "Round 3" ~ "Emergency Midfielder",
             player_name_full == "Lachie Hunter" & round_number == "Round 3" ~ "Emergency Midfielder",
             
             player_name_full == "Brad Close" & round_number == "Round 4" ~ "Emergency Forward",
             player_name_full == "Brayden Maynard" & round_number == "Round 4" ~ "Emergency Defender",
             player_name_full == "Charlie Cameron" & round_number == "Round 4" ~ "Emergency Forward",
             player_name_full == "Angus Brayshaw" & round_number == "Round 4" ~ "Emergency Midfielder",
             player_name_full == "Riley Bonner" & round_number == "Round 4" ~ "Emergency Defender",
             player_name_full == "Oliver Florent" & round_number == "Round 4" ~ "Emergency Midfielder",
             player_name_full == "Steven May" & round_number == "Round 4" ~ "Emergency Defender",
             player_name_full == "Callum Wilkie" & round_number == "Round 4" ~ "Emergency Defender",
             player_name_full == "David Mundy" & round_number == "Round 4" ~ "Emergency Midfielder",
             
             player_name_full == "Tim Membrey" & round_number == "Round 5" ~ "Emergency Forward",
             player_name_full == "Brandon Ellis" & round_number == "Round 5" ~ "Emergency Midfielder",
             player_name_full == "Taylor Walker" & round_number == "Round 5" ~ "Emergency Forward",
             player_name_full == "Charlie Cameron" & round_number == "Round 5" ~ "Emergency Forward",
             
             player_name_full == "Sebastian Ross" & round_number == "Round 6" ~ "Emergency Midfielder",
             player_name_full == "Steele Sidebottom" & round_number == "Round 6" ~ "Emergency Midfielder",
             player_name_full == "Josh Battle" & round_number == "Round 6" ~ "Emergency Forward",
             player_name_full == "Kane Farrell" & round_number == "Round 6" ~ "Emergency Forward",
             
             player_name_full == "Kane Lambert" & round_number == "Round 7" ~ "Emergency Forward",
             player_name_full == "Stefan Martin" & round_number == "Round 7" ~ "Emergency Ruck",
             player_name_full == "Jack Redden" & round_number == "Round 7" ~ "Emergency Midfielder",
             player_name_full == "Jeremy Cameron" & round_number == "Round 7" ~ "Emergency Forward",
             player_name_full == "Charlie Curnow" & round_number == "Round 7" ~ "Emergency Forward",
             
             player_name_full == "David Mundy" & round_number == "Round 8" ~ "Emergency Midfielder",
             player_name_full == "Jye Caldwell" & round_number == "Round 8" ~ "Emergency Midfielder",
             player_name_full == "Jordan Clark" & round_number == "Round 8" ~ "Emergency Midfielder",
             player_name_full == "Brayden Maynard" & round_number == "Round 8" ~ "Emergency Defender",
             player_name_full == "Will Day" & round_number == "Round 8" ~ "Emergency Defender",
             player_name_full == "Luke McDonald" & round_number == "Round 8" ~ "Emergency Defender",
             player_name_full == "Tarryn Thomas" & round_number == "Round 8" ~ "Emergency Forward",
             player_name_full == "Chad Warner" & round_number == "Round 8" ~ "Emergency Midfielder",
             player_name_full == "Darcy Cameron" & round_number == "Round 8" ~ "Emergency Forward",
             player_name_full == "Mason Redman" & round_number == "Round 8" ~ "Emergency Defender",
             
             player_name_full == "Tom J. Lynch" & round_number == "Round 9" ~ "Emergency Forward",
             player_name_full == "Jeremy Howe" & round_number == "Round 9" ~ "Emergency Defender",
             player_name_full == "Zach Tuohy" & round_number == "Round 9" ~ "Emergency Midfielder",
             player_name_full == "Rhys Stanley" & round_number == "Round 9" ~ "Emergency Ruck",
             player_name_full == "Jarman Impey" & round_number == "Round 9" ~ "Emergency Defender",
             
             player_name_full == "Luke McDonald" & round_number == "Round 10" ~ "Emergency Defender",
             player_name_full == "Jeremy Cameron" & round_number == "Round 10" ~ "Emergency Forward",
             player_name_full == "Mason Redman" & round_number == "Round 10" ~ "Emergency Defender",
             player_name_full == "Nic Newman" & round_number == "Round 10" ~ "Emergency Defender",
             player_name_full == "Jackson Hately" & round_number == "Round 10" ~ "Emergency Midfielder",
             player_name_full == "Jai Newcombe" & round_number == "Round 10" ~ "Emergency Midfielder",
             player_name_full == "Tom Atkins" & round_number == "Round 10" ~ "Emergency Defender",
             
             player_name_full == "Bradley Hill" & round_number == "Round 11" ~ "Emergency Defender",
             player_name_full == "Jack Graham" & round_number == "Round 11" ~ "Emergency Forward",
             player_name_full == "Tom Hawkins" & round_number == "Round 11" ~ "Emergency Forward",
             player_name_full == "Chad Warner" & round_number == "Round 11" ~ "Emergency Midfielder",
             player_name_full == "Tarryn Thomas" & round_number == "Round 11" ~ "Emergency Midfielder",
             player_name_full == "Nathan Broad" & round_number == "Round 11" ~ "Emergency Defender",
             
             player_name_full == "Nick Hind" & round_number == "Round 15" ~ "Emergency Defender",
             player_name_full == "Jack Newnes" & round_number == "Round 15" ~ "Emergency Midfielder",
             player_name_full == "Liam Duggan" & round_number == "Round 15" ~ "Emergency Defender",
             player_name_full == "Sam Powell-Pepper" & round_number == "Round 15" ~ "Emergency Midfielder",
             player_name_full == "Mitch Lewis" & round_number == "Round 15" ~ "Emergency Forward",
             
             player_name_full == "Bradley Hill" & round_number == "Round 16" ~ "Emergency Defender",
             player_name_full == "Jaeger O'Meara" & round_number == "Round 16" ~ "Emergency Midfielder",
             player_name_full == "Rowan Marshall" & round_number == "Round 16" ~ "Emergency Ruck",
             player_name_full == "David Swallow" & round_number == "Round 16" ~ "Emergency Defender",
             player_name_full == "Nic Martin" & round_number == "Round 16" ~ "Emergency Forward",
             player_name_full == "Jackson Hately" & round_number == "Round 16" ~ "Emergency Midfielder",
             player_name_full == "Tom Hickey" & round_number == "Round 16" ~ "Emergency Ruck",
             player_name_full == "Keidean Coleman" & round_number == "Round 16" ~ "Emergency Forward",
             player_name_full == "Mason Redman" & round_number == "Round 16" ~ "Emergency Defender",
             player_name_full == "Justin McInerney" & round_number == "Round 16" ~ "Emergency Defender",
             player_name_full == "Jack Bowes" & round_number == "Round 16" ~ "Emergency Defender",
             player_name_full == "David Mundy" & round_number == "Round 16" ~ "Emergency Midfielder",
             
             player_name_full == "Lance Franklin" & round_number == "Round 17" ~ "Emergency Forward",
             player_name_full == "Josh Daicos" & round_number == "Round 17" ~ "Emergency Midfielder",
             player_name_full == "Sam Powell-Pepper" & round_number == "Round 17" ~ "Emergency Midfielder"
           )
         )

all_fielded_teams_full <-
  all_fielded_teams_full %>%
  mutate(fielded_position = ifelse(!is.na(fielded_position_2), fielded_position_2, fielded_position)) %>%
  select(-fielded_position_2)

#===============================================================================
# Get details for players who didn't play any games from player data table
#===============================================================================

names_to_join <-
  player_details %>%
  filter(player_name %notin% all_fielded_teams_full$player_name_full) %>%
  select(player_name, club = team, height, weight, dob) %>%
  mutate(
    player_first_initial = str_extract(player_name, "^[A-Z]"),
    player_last_name = str_extract(player_name, "[A-Za-z-']*$"),
    player_name_initials = paste(player_first_initial,
                                 ". ",
                                 player_last_name,
                                 sep = "")) %>%
  select(-player_first_initial, -player_last_name) %>%
  mutate(player_name_initials = ifelse(player_name == "Liam Jones", "Liam Jones", player_name_initials)) %>% # Manually fix case of liam jones and lachie jones
  mutate(player_name_initials = ifelse(player_name == "Josh J. Kennedy", "Josh J. Kennedy", player_name_initials)) %>% # Manually fix case of Josh J. Kennedy
  filter(player_name_initials %in% all_fielded_teams_full$player_name) %>%
  filter(player_name_initials %notin% c("T. Lynch", "C. Warner", "C. Brown", "S. Darcy", "Z. Williams")) # Manually filter out duplicate players who didn't get picked for whole year

#===============================================================================
# Join to main table, coalesce to get rid of NAs and remove new columns
#===============================================================================

all_fielded_teams_full <-
  all_fielded_teams_full %>%
  left_join(names_to_join, by = c("player_name" = "player_name_initials")) %>%
  mutate(
    player_name_full = coalesce(player_name_full, player_name.y),
    club.x = coalesce(club.x, club.y),
    height.x = coalesce(height.x, height.y),
    weight.x = coalesce(weight.x, weight.y),
    dob.x = coalesce(dob.x, dob.y)) %>%
  rename(club = club.x,
         height = height.x,
         weight = weight.x,
         dob = dob.x) %>%
  select(-player_name.y,
         -club.y,
         -height.y,
         -weight.y,
         -dob.y) %>% 
  group_by(player_name) %>%
  fill(player_name_full, club, height, weight, dob, .direction = "downup") %>%
  rename(round_start_date = start_time) %>%
  group_by(round_number) %>%
  mutate(round_start_date = as.Date(min(round_start_date, na.rm = TRUE))) %>%
  ungroup() %>%
  mutate(player_age_at_round_start = round(as.numeric((round_start_date - dob) / 365.25), digits = 2))

##%######################################################%##
#                                                          #
####          Replace NA fantasy points with 0          ####
#                                                          #
##%######################################################%##

all_fielded_teams_full <-
all_fielded_teams_full %>%
  replace_na(replace = list(fantasy_points = 0))

##%######################################################%##
#                                                          #
####      Create variables for if a player played       ####
####             in a game, if they had an              ####
####          onfield injury with < 50 TOG, if          ####
####  there was an emergency present for each position  ####
#                                                          #
##%######################################################%##

all_fielded_teams_full <-
all_fielded_teams_full %>%
  mutate(
    played_game = ifelse(TOG == 0 | is.na(TOG), FALSE, TRUE),
    onfield_injury = ifelse(TOG > 0 & TOG < 50, TRUE, FALSE)) %>%
    group_by(fantasy_team, round_number) %>%
  mutate(
    emergency_defender_present = ifelse(max(fielded_position == "Emergency Defender", na.rm = TRUE) == 1, TRUE, FALSE),
    emergency_midfielder_present = ifelse(max(fielded_position == "Emergency Midfielder", na.rm = TRUE) == 1, TRUE, FALSE),
    emergency_ruck_present = ifelse(max(fielded_position == "Emergency Ruck", na.rm = TRUE) == 1, TRUE, FALSE),
    emergency_forward_present = ifelse(max(fielded_position == "Emergency Forward", na.rm = TRUE) == 1, TRUE, FALSE)) %>%
  ungroup() %>%
  mutate(injury_substituted = ifelse(onfield_injury & emergency_defender_present & fielded_position == "Defender", TRUE, FALSE)) %>%
  mutate(injury_substituted = ifelse(onfield_injury & emergency_midfielder_present & fielded_position == "Midfielder", TRUE, injury_substituted)) %>%
  mutate(injury_substituted = ifelse(onfield_injury & emergency_ruck_present & fielded_position == "Ruck", TRUE, injury_substituted)) %>%
  mutate(injury_substituted = ifelse(onfield_injury & emergency_forward_present & fielded_position == "Forward", TRUE, injury_substituted))

##%######################################################%##
#                                                          #
#### Deal with special case where a player was injured  ####
####      on field but a sub has already been used      ####
#                                                          #
##%######################################################%##

all_fielded_teams_full <-
all_fielded_teams_full %>%
  group_by(fantasy_team, round_number) %>%
  mutate(number_of_onfield_injured_mids = sum((onfield_injury | is.na(TOG) | TOG == 0) & fielded_position == "Midfielder", na.rm = TRUE),
         number_of_onfield_injured_defs = sum((onfield_injury | is.na(TOG) | TOG == 0) & fielded_position == "Defender", na.rm = TRUE),
         number_of_onfield_injured_fwds = sum((onfield_injury | is.na(TOG) | TOG == 0) & fielded_position == "Forward", na.rm = TRUE)) %>%
  group_by(fantasy_team, round_number, fielded_position) %>%
  mutate(
    injury_substituted = ifelse(
      onfield_injury &
        fielded_position == "Midfielder" &
        number_of_onfield_injured_mids > 1 &
        fantasy_points != min(fantasy_points), FALSE, injury_substituted)) %>%
  mutate(
    injury_substituted = ifelse(
      onfield_injury &
        fielded_position == "Defender" &
        number_of_onfield_injured_defs > 1 &
        fantasy_points != min(fantasy_points), FALSE, injury_substituted)) %>%
  mutate(
    injury_substituted = ifelse(
      onfield_injury &
        fielded_position == "Forward" &
        number_of_onfield_injured_fwds > 1 &
        fantasy_points != min(fantasy_points), FALSE, injury_substituted)) %>%
  select(-number_of_onfield_injured_mids, -number_of_onfield_injured_defs, -number_of_onfield_injured_fwds) %>%
  ungroup()
  
##%######################################################%##
#                                                          #
#### Fix special case where Wines and Cripps were both  ####
####                injured on the same                 ####
####       score (round 4, putin's peacekeepers)        ####
#                                                          #
##%######################################################%##

all_fielded_teams_full <-
  all_fielded_teams_full %>%
  mutate(injury_substituted = ifelse(player_name == "P. Cripps" & round_number == "Round 4", FALSE, injury_substituted))

##%######################################################%##
#                                                          #
####       Add player season average to the table       ####
#                                                          #
##%######################################################%##

season_averages <-
combined_stats_table %>%
  filter(TOG > 50) %>%
  group_by(player_name) %>%
  summarise(average_score = round(mean(fantasy_points, na.rm = TRUE), digits = 2))

all_fielded_teams_full <-
  all_fielded_teams_full %>%
  left_join(season_averages, by = c("player_name_full" = "player_name"))

```

## 10 Highest and Lowest Fielded Scores

::: panel-tabset

## Highest

```{r}
all_fielded_teams_full %>% 
  select(player_name_full,
         fantasy_points,
         fantasy_team,
         round_number,
         fielded_position) %>%
  arrange(desc(fantasy_points)) %>%
  head(10)
```


## Lowest (Injuries and Non-playing players excluded)

```{r}
all_fielded_teams_full %>%
  filter(!injury_substituted & fielded_position != "Interchange") %>%
  filter(TOG > 50) %>%
  select(player_name_full,
         fantasy_points,
         TOG,
         fantasy_team,
         round_number,
         fielded_position) %>%
  arrange(fantasy_points) %>%
  head(10)
```

:::

## Highest and Lowest Fielded Score by Team

::: panel-tabset

## Highest

```{r}
all_fielded_teams_full %>% 
  select(fantasy_team,
         fantasy_points,
         player_name_full,
         round_number,
         fielded_position) %>%
  arrange(desc(fantasy_points)) %>%
  group_by(fantasy_team) %>%
  filter(row_number() == min(row_number()))
```

## Lowest (Injuries and Non-playing players excluded)

```{r}
all_fielded_teams_full %>%
  filter(!injury_substituted & fielded_position != "Interchange") %>%
  filter(TOG > 60) %>%
  select(fantasy_team,
         fantasy_points,
         TOG,
         player_name_full,
         round_number,
         fielded_position) %>%
  arrange(fantasy_points) %>%
  group_by(fantasy_team) %>%
  filter(row_number() == min(row_number()))
```

:::

## Biggest Outlier Scores

```{r}
all_fielded_teams_full %>%
  select(fantasy_team,
         fantasy_points,
         player_name_full,
         round_number,
         fielded_position,
         average_score) %>%
  mutate(diff = fantasy_points - average_score) %>%
  arrange(desc(diff)) %>%
  head(20)
```

## Smallest Outlier Scores (Injuries excluded)

```{r}
all_fielded_teams_full %>%
  filter(fielded_position != "Interchange" & TOG > 50) %>%
  select(fantasy_team,
         fantasy_points,
         player_name_full,
         round_number,
         fielded_position,
         average_score) %>%
  mutate(diff = fantasy_points - average_score) %>%
  arrange(diff) %>%
  head(20)
```

## Biggest Loopholed Scores

```{r}
all_fielded_teams_full %>% 
  filter(str_detect(fielded_position, "Emergency")) %>%
  select(player_name_full,
         fantasy_points,
         fantasy_team,
         round_number,
         fielded_position) %>%
  arrange(desc(fantasy_points)) %>%
  head(20)
```

## Smallest Loopholed Scores

```{r}
all_fielded_teams_full %>% 
  filter(str_detect(fielded_position, "Emergency")) %>%
  select(player_name_full,
         fantasy_points,
         fantasy_team,
         round_number,
         fielded_position) %>%
  arrange(fantasy_points) %>%
  head(20)
```

## Loophole usage and performance

```{r}
# loophole performance
  all_fielded_teams_full %>% 
  filter(str_detect(fielded_position, "Emergency") | injury_substituted) %>%
  group_by(fantasy_team, round_number) %>%
  mutate(defender_sub_activated = sum(injury_substituted & fielded_position == "Defender"),
         midfielder_sub_activated = sum(injury_substituted & fielded_position == "Midfielder"),
         ruck_sub_activated = sum(injury_substituted & fielded_position == "Ruck"),
         forward_sub_activated = sum(injury_substituted & fielded_position == "Forward")
         ) %>%
  ungroup() %>%
  filter(str_detect(fielded_position, "Emergency")) %>%
  filter(!(fielded_position == "Emergency Defender" & defender_sub_activated > 0)) %>%
  filter(!(fielded_position == "Emergency Midfielder" & midfielder_sub_activated > 0)) %>%
  filter(!(fielded_position == "Emergency Ruck" & ruck_sub_activated > 0)) %>%
  filter(!(fielded_position == "Emergency Forward" & forward_sub_activated > 0)) %>%
  group_by(fantasy_team) %>%
  summarise(avg_loopholed_score = round(mean(fantasy_points, na.rm = TRUE), 2), number_of_loopholes_used = n()) %>%
  arrange(desc(number_of_loopholes_used))

```

## Full team not fielded

```{r}
    all_fielded_teams_full %>% 
  filter(fielded_position != "Interchange" & !injury_substituted & TOG != 0 & !is.na(TOG)) %>%
  group_by(fantasy_team, round_number) %>%
  mutate(players_fielded = n()) %>%
  ungroup() %>%
  distinct(fantasy_team, round_number, .keep_all = TRUE) %>%
  group_by(fantasy_team) %>%
  summarise(num_of_non_full_teams = sum(players_fielded < 18, na.rm = TRUE))
```

