---
title: "Heatmaps"
subtitle: "2022 Season"
format:
  html:
      theme: cosmo
      self-contained: true
      toc: true
      fig-width: 8
      fig-height: 6
editor: visual
author: James Brown
---

```{r}
#| label: load-packages-and-data
#| include: false
#| message: false

# Libraries and Data
library(tidyverse)
library(ggthemes)
library(paletteer)
combined_stats_table <- read_rds("../../../Data/RDS-files/combined_stats_table_2021.rds")
```

```{r}
#| label: cba-heatmap-function
#| include: false
#| message: false

create_cba_heatmap <- function(team_name){
heatmap_df_cbas <-
combined_stats_table %>%
  filter(team == team_name) %>%
  select(player_name, round_number, CBA_percentage) %>%
  group_by(player_name) %>%
  filter(max(CBA_percentage, na.rm = TRUE) > 0) %>%
  mutate(mean_CBA_percentage = mean(CBA_percentage, na.rm = TRUE)) %>%
  arrange(desc(mean_CBA_percentage), player_name)

heatmap_plot_cba <-
ggplot(heatmap_df_cbas, aes(round_number, reorder(player_name, mean_CBA_percentage), fill = CBA_percentage)) +
  geom_tile() +
  scale_x_discrete(guide = guide_axis(angle=90)) +
  xlab("Round") + 
  ylab("Player") +
  labs(fill = "CBA %") +
  scale_fill_paletteer_c(`"viridis::plasma"`) +
  theme_tufte(ticks = FALSE) +
  geom_vline(xintercept = seq(0.5,length(unique(combined_stats_table$round_number)) - 0.5, by = 1), colour = "grey50") +
  geom_hline(yintercept = seq(0.5, length(unique(heatmap_df_cbas$player_name)) + 0.5, by = 1), colour = "grey50") +
  theme(panel.background = element_rect(fill = "darkblue",colour = "white")) +
geom_vline(xintercept = seq(length(unique(combined_stats_table$round_number)) - 0.495, length(unique(combined_stats_table$round_number)) - 0.4, by = 0.01), colour = "white") +  geom_vline(xintercept = seq(0.40, 0.48, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(length(unique(heatmap_df_cbas$player_name)) + 0.52, length(unique(heatmap_df_cbas$player_name)) + 1.5, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(0.4, 0.45, by = 0.01), colour = "white") +
  geom_text(mapping = aes(label = round(CBA_percentage, 1)), size = 3,
            colour = case_when(heatmap_df_cbas$CBA_percentage > 70 ~ "black", heatmap_df_cbas$CBA_percentage <= 70 ~ "white"), fontface = "bold")

print(heatmap_plot_cba)
}

```

```{r}
#| label: kickin-heatmap-function
#| include: false
#| message: false

create_kickin_heatmap <- function(team_name){
heatmap_df_kickins <-
combined_stats_table %>%
  filter(team == team_name) %>%
  select(player_name, round_number, kick_in_percentage) %>%
  group_by(player_name) %>%
  filter(max(kick_in_percentage, na.rm = TRUE) > 0) %>%
  mutate(mean_kick_in_percentage = mean(kick_in_percentage, na.rm = TRUE)) %>%
  arrange(desc(mean_kick_in_percentage), player_name)

heatmap_plot_kickin <-
ggplot(heatmap_df_kickins, aes(round_number, reorder(player_name, mean_kick_in_percentage), fill = kick_in_percentage)) +
  geom_tile() +
  scale_x_discrete(guide = guide_axis(angle=90)) +
  xlab("Round") + 
  ylab("Player") +
  labs(fill = "Kick-in %") +
  scale_fill_paletteer_c(`"viridis::plasma"`) +
  theme_tufte(ticks = FALSE) +
  geom_vline(xintercept = seq(0.5,length(unique(combined_stats_table$round_number)) - 0.5, by = 1), colour = "grey50") +
  geom_hline(yintercept = seq(0.5, length(unique(heatmap_df_kickins$player_name)) + 0.5, by = 1), colour = "grey50") +
  theme(panel.background = element_rect(fill = "darkblue",colour = "white")) +
geom_vline(xintercept = seq(length(unique(combined_stats_table$round_number)) - 0.495, length(unique(combined_stats_table$round_number)) - 0.4, by = 0.01), colour = "white") +  geom_vline(xintercept = seq(0.40, 0.48, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(length(unique(heatmap_df_kickins$player_name)) + 0.52, length(unique(heatmap_df_kickins$player_name)) + 1.5, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(0.4, 0.45, by = 0.01), colour = "white") +
  geom_text(mapping = aes(label = round(kick_in_percentage, 1)), size = 3,
            colour = case_when(heatmap_df_kickins$kick_in_percentage > 45 ~ "black", heatmap_df_kickins$kick_in_percentage <= 45 ~ "white"), fontface = "bold")

print(heatmap_plot_kickin)
}

```

```{r}
#| label: uncontested-mark-heatmap-function
#| include: false
#| message: false

create_uncontested_mark_heatmap <- function(team_name) {
  heatmap_df_uncontested_marks <-
    combined_stats_table %>%
    group_by(team, round_number) %>%
    mutate(total_uncontested_marks = sum(uncontestedMarks)) %>%
    ungroup() %>%
    mutate(uncontested_marks_percentage = round((
      uncontestedMarks / total_uncontested_marks
    ) * 100, digits = 2)) %>%
  filter(team == team_name) %>%
    select(player_name, round_number, uncontested_marks_percentage) %>%
    group_by(player_name) %>%
    filter(max(uncontested_marks_percentage, na.rm = TRUE) > 0) %>%
    mutate(mean_uncontested_marks_percentage = mean(uncontested_marks_percentage, na.rm = TRUE)) %>%
    arrange(desc(mean_uncontested_marks_percentage), player_name)

heatmap_plot_uncontested_mark <-
ggplot(heatmap_df_uncontested_marks, aes(round_number, reorder(player_name, mean_uncontested_marks_percentage), fill = uncontested_marks_percentage)) +
  geom_tile() +
  scale_x_discrete(guide = guide_axis(angle=90)) +
  xlab("Round") + 
  ylab("Player") +
  labs(fill = "Uncontested Mark %") +
  scale_fill_paletteer_c(`"viridis::plasma"`) +
  theme_tufte(ticks = FALSE) +
  geom_vline(xintercept = seq(0.5,length(unique(combined_stats_table$round_number)) - 0.5, by = 1), colour = "grey50") +
  geom_hline(yintercept = seq(0.5, length(unique(heatmap_df_uncontested_marks$player_name)) + 0.5, by = 1), colour = "grey50") +
  theme(panel.background = element_rect(fill = "darkblue",colour = "white")) +
geom_vline(xintercept = seq(length(unique(combined_stats_table$round_number)) - 0.495, length(unique(combined_stats_table$round_number)) - 0.4, by = 0.01), colour = "white") +  geom_vline(xintercept = seq(0.40, 0.48, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(length(unique(heatmap_df_uncontested_marks$player_name)) + 0.52, length(unique(heatmap_df_uncontested_marks$player_name)) + 1.5, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(0.4, 0.45, by = 0.01), colour = "white") +
  geom_text(mapping = aes(label = round(uncontested_marks_percentage, 1)), size = 3,
            colour = case_when(heatmap_df_uncontested_marks$uncontested_marks_percentage > 8 ~ "black", heatmap_df_uncontested_marks$uncontested_marks_percentage <= 8 ~ "white"), fontface = "bold")

print(heatmap_plot_uncontested_mark)
}

```

```{r}
#| label: rebound-50-heatmap-function
#| include: false
#| message: false

create_rebound_50_heatmap <- function(team_name) {
  heatmap_df_rebound_50s <-
    combined_stats_table %>%
    group_by(team, round_number) %>%
    mutate(total_rebound_50s = sum(rebound50s)) %>%
  ungroup() %>%
  mutate(rebound_50s_percentage = round((rebound50s / total_rebound_50s)*100, digits = 2)) %>%
  filter(team == team_name) %>%
    select(player_name, round_number, rebound_50s_percentage) %>%
    group_by(player_name) %>%
    filter(max(rebound_50s_percentage, na.rm = TRUE) > 0) %>%
    mutate(mean_rebound_50s_percentage = mean(rebound_50s_percentage, na.rm = TRUE)) %>%
    arrange(desc(mean_rebound_50s_percentage), player_name)

heatmap_plot_rebound_50 <-
ggplot(heatmap_df_rebound_50s, aes(round_number, reorder(player_name, mean_rebound_50s_percentage), fill = rebound_50s_percentage)) +
  geom_tile() +
  scale_x_discrete(guide = guide_axis(angle=90)) +
  xlab("Round") + 
  ylab("Player") +
  labs(fill = "Rebound 50 %") +
  scale_fill_paletteer_c(`"viridis::plasma"`) +
  theme_tufte(ticks = FALSE) +
  geom_vline(xintercept = seq(0.5,length(unique(combined_stats_table$round_number)) - 0.5, by = 1), colour = "grey50") +
  geom_hline(yintercept = seq(0.5, length(unique(heatmap_df_rebound_50s$player_name)) + 0.5, by = 1), colour = "grey50") +
  theme(panel.background = element_rect(fill = "darkblue",colour = "white")) +
geom_vline(xintercept = seq(length(unique(combined_stats_table$round_number)) - 0.495, length(unique(combined_stats_table$round_number)) - 0.4, by = 0.01), colour = "white") +  geom_vline(xintercept = seq(0.40, 0.48, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(length(unique(heatmap_df_rebound_50s$player_name)) + 0.52, length(unique(heatmap_df_rebound_50s$player_name)) + 1.5, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(0.4, 0.45, by = 0.01), colour = "white") +
  geom_text(mapping = aes(label = round(rebound_50s_percentage, 1)), size = 3,
            colour = case_when(heatmap_df_rebound_50s$rebound_50s_percentage > 20 ~ "black", heatmap_df_rebound_50s$rebound_50s_percentage <= 20 ~ "white"), fontface = "bold")

print(heatmap_plot_rebound_50)
}

```

```{r}
#| label: fantasy-points-heatmap-function
#| include: false
#| message: false

create_fantasy_point_heatmap <- function(team_name) {
    heatmap_df_fantasy_points <-
    combined_stats_table %>%
    filter(team == team_name) %>%
    select(player_name, round_number, fantasy_points) %>%
    group_by(player_name) %>%
    mutate(mean_fantasy_points = mean(fantasy_points, na.rm = TRUE)) %>%
    arrange(desc(mean_fantasy_points), player_name) %>%
    filter(mean_fantasy_points > 60)

heatmap_plot_fantasy_point <-
ggplot(heatmap_df_fantasy_points, aes(round_number, reorder(player_name, mean_fantasy_points), fill = fantasy_points)) +
  geom_tile() +
  scale_x_discrete(guide = guide_axis(angle=90)) +
  xlab("Round") + 
  ylab("Player") +
  labs(fill = "Fantasy Points") +
  scale_fill_paletteer_c(`"viridis::plasma"`) +
  theme_tufte(ticks = FALSE) +
  geom_vline(xintercept = seq(0.5,length(unique(combined_stats_table$round_number)) - 0.5, by = 1), colour = "grey50") +
  geom_hline(yintercept = seq(0.5, length(unique(heatmap_df_fantasy_points$player_name)) + 0.5, by = 1), colour = "grey50") +
  theme(panel.background = element_rect(fill = "darkblue",colour = "white")) +
  geom_vline(xintercept = seq(length(unique(combined_stats_table$round_number)) - 0.495, length(unique(combined_stats_table$round_number)) - 0.4, by = 0.01), colour = "white") +
  geom_vline(xintercept = seq(0.40, 0.48, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(length(unique(heatmap_df_fantasy_points$player_name)) + 0.52, length(unique(heatmap_df_fantasy_points$player_name)) + 1.5, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(0.4, 0.45, by = 0.01), colour = "white") +
  geom_text(mapping = aes(label = round(fantasy_points, 1)), size = 3,
            colour = case_when(heatmap_df_fantasy_points$fantasy_points > 100 ~ "black", heatmap_df_fantasy_points$fantasy_points <= 100 ~ "white"), fontface = "bold")

print(heatmap_plot_fantasy_point)
}

```

```{r}
#| label: goals-heatmap-function
#| include: false
#| message: false

create_goal_heatmap <- function(team_name) {
    heatmap_df_goals <-
    combined_stats_table %>%
    filter(team == team_name) %>%
    select(player_name, round_number, goals) %>%
    group_by(player_name) %>%
    mutate(mean_goals = mean(goals, na.rm = TRUE)) %>%
    arrange(desc(mean_goals), player_name) %>%
    filter(mean_goals > 0.5)

heatmap_plot_goal <-
ggplot(heatmap_df_goals, aes(round_number, reorder(player_name, mean_goals), fill = goals)) +
  geom_tile() +
  scale_x_discrete(guide = guide_axis(angle=90)) +
  xlab("Round") + 
  ylab("Player") +
  labs(fill = "Goals") +
  scale_fill_paletteer_c(`"viridis::plasma"`) +
  theme_tufte(ticks = FALSE) +
  geom_vline(xintercept = seq(0.5,length(unique(combined_stats_table$round_number)) - 0.5, by = 1), colour = "grey50") +
  geom_hline(yintercept = seq(0.5, length(unique(heatmap_df_goals$player_name)) + 0.5, by = 1), colour = "grey50") +
  theme(panel.background = element_rect(fill = "darkblue",colour = "white")) +
geom_vline(xintercept = seq(length(unique(combined_stats_table$round_number)) - 0.495, length(unique(combined_stats_table$round_number)) - 0.4, by = 0.01), colour = "white") +  geom_vline(xintercept = seq(0.40, 0.48, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(length(unique(heatmap_df_goals$player_name)) + 0.52, length(unique(heatmap_df_goals$player_name)) + 1.5, by = 0.01), colour = "white") +
  geom_hline(yintercept = seq(0.4, 0.48, by = 0.01), colour = "white") +
  geom_text(mapping = aes(label = round(goals, 1)), size = 3,
            colour = case_when(heatmap_df_goals$goals > 3 ~ "black", heatmap_df_goals$goals <= 3 ~ "white"), fontface = "bold")

print(heatmap_plot_goal)
}

```

## Fantasy Points

##### (Among Players who average over 60 for the season)

::: panel-tabset
## Adelaide Crows

```{r}
#| echo: false
create_fantasy_point_heatmap("Adelaide Crows")
```

## Brisbane Lions

```{r}
#| echo: false
create_fantasy_point_heatmap("Brisbane Lions")
```

## Carlton

```{r}
#| echo: false
create_fantasy_point_heatmap("Carlton")
```

## Collingwood

```{r}
#| echo: false
create_fantasy_point_heatmap("Collingwood")
```

## Essendon

```{r}
#| echo: false
create_fantasy_point_heatmap("Essendon")
```

## Fremantle

```{r}
#| echo: false
create_fantasy_point_heatmap("Fremantle")
```

## Geelong Cats

```{r}
#| echo: false
create_fantasy_point_heatmap("Geelong Cats")
```

## Gold Coast Suns

```{r}
#| echo: false
create_fantasy_point_heatmap("Gold Coast Suns")
```

## GWS Giants

```{r}
#| echo: false
create_fantasy_point_heatmap("GWS Giants")
```

## Hawthorn

```{r}
#| echo: false
create_fantasy_point_heatmap("Hawthorn")
```

## Melbourne

```{r}
#| echo: false
create_fantasy_point_heatmap("Melbourne")
```

## North Melbourne

```{r}
#| echo: false
create_fantasy_point_heatmap("North Melbourne")
```

## Port Adelaide

```{r}
#| echo: false
create_fantasy_point_heatmap("Port Adelaide")
```

## Richmond

```{r}
#| echo: false
create_fantasy_point_heatmap("Richmond")
```

## St Kilda

```{r}
#| echo: false
create_fantasy_point_heatmap("St Kilda")
```

## Sydney Swans

```{r}
#| echo: false
create_fantasy_point_heatmap("Sydney Swans")
```

## West Coast Eagles

```{r}
#| echo: false
create_fantasy_point_heatmap("West Coast Eagles")
```

## Western Bulldogs

```{r}
#| echo: false
create_fantasy_point_heatmap("Western Bulldogs")
```
:::

## Centre Bounce Attendances

##### (Player's Percentage of Total CBAs for the Match)

::: panel-tabset
## Adelaide Crows

```{r}
#| echo: false
create_cba_heatmap("Adelaide Crows")
```

## Brisbane Lions

```{r}
#| echo: false
create_cba_heatmap("Brisbane Lions")
```

## Carlton

```{r}
#| echo: false
create_cba_heatmap("Carlton")
```

## Collingwood

```{r}
#| echo: false
create_cba_heatmap("Collingwood")
```

## Essendon

```{r}
#| echo: false
create_cba_heatmap("Essendon")
```

## Fremantle

```{r}
#| echo: false
create_cba_heatmap("Fremantle")
```

## Geelong Cats

```{r}
#| echo: false
create_cba_heatmap("Geelong Cats")
```

## Gold Coast Suns

```{r}
#| echo: false
create_cba_heatmap("Gold Coast Suns")
```

## GWS Giants

```{r}
#| echo: false
create_cba_heatmap("GWS Giants")
```

## Hawthorn

```{r}
#| echo: false
create_cba_heatmap("Hawthorn")
```

## Melbourne

```{r}
#| echo: false
create_cba_heatmap("Melbourne")
```

## North Melbourne

```{r}
#| echo: false
create_cba_heatmap("North Melbourne")
```

## Port Adelaide

```{r}
#| echo: false
create_cba_heatmap("Port Adelaide")
```

## Richmond

```{r}
#| echo: false
create_cba_heatmap("Richmond")
```

## St Kilda

```{r}
#| echo: false
create_cba_heatmap("St Kilda")
```

## Sydney Swans

```{r}
#| echo: false
create_cba_heatmap("Sydney Swans")
```

## West Coast Eagles

```{r}
#| echo: false
create_cba_heatmap("West Coast Eagles")
```

## Western Bulldogs

```{r}
#| echo: false
create_cba_heatmap("Western Bulldogs")
```
:::

## Kick-ins

##### (Player's Percentage of Total Kick-ins for the Match)

::: panel-tabset
## Adelaide Crows

```{r}
#| echo: false
create_kickin_heatmap("Adelaide Crows")
```

## Brisbane Lions

```{r}
#| echo: false
create_kickin_heatmap("Brisbane Lions")
```

## Carlton

```{r}
#| echo: false
create_kickin_heatmap("Carlton")
```

## Collingwood

```{r}
#| echo: false
create_kickin_heatmap("Collingwood")
```

## Essendon

```{r}
#| echo: false
create_kickin_heatmap("Essendon")
```

## Fremantle

```{r}
#| echo: false
create_kickin_heatmap("Fremantle")
```

## Geelong Cats

```{r}
#| echo: false
create_kickin_heatmap("Geelong Cats")
```

## Gold Coast Suns

```{r}
#| echo: false
create_kickin_heatmap("Gold Coast Suns")
```

## GWS Giants

```{r}
#| echo: false
create_kickin_heatmap("GWS Giants")
```

## Hawthorn

```{r}
#| echo: false
create_kickin_heatmap("Hawthorn")
```

## Melbourne

```{r}
#| echo: false
create_kickin_heatmap("Melbourne")
```

## North Melbourne

```{r}
#| echo: false
create_kickin_heatmap("North Melbourne")
```

## Port Adelaide

```{r}
#| echo: false
create_kickin_heatmap("Port Adelaide")
```

## Richmond

```{r}
#| echo: false
create_kickin_heatmap("Richmond")
```

## St Kilda

```{r}
#| echo: false
create_kickin_heatmap("St Kilda")
```

## Sydney Swans

```{r}
#| echo: false
create_kickin_heatmap("Sydney Swans")
```

## West Coast Eagles

```{r}
#| echo: false
create_kickin_heatmap("West Coast Eagles")
```

## Western Bulldogs

```{r}
#| echo: false
create_kickin_heatmap("Western Bulldogs")
```
:::

## Uncontested Marks

##### (Player's Percentage of Uncontested Marks for the Match)

::: panel-tabset
## Adelaide Crows

```{r}
#| echo: false
create_uncontested_mark_heatmap("Adelaide Crows")
```

## Brisbane Lions

```{r}
#| echo: false
create_uncontested_mark_heatmap("Brisbane Lions")
```

## Carlton

```{r}
#| echo: false
create_uncontested_mark_heatmap("Carlton")
```

## Collingwood

```{r}
#| echo: false
create_uncontested_mark_heatmap("Collingwood")
```

## Essendon

```{r}
#| echo: false
create_uncontested_mark_heatmap("Essendon")
```

## Fremantle

```{r}
#| echo: false
create_uncontested_mark_heatmap("Fremantle")
```

## Geelong Cats

```{r}
#| echo: false
create_uncontested_mark_heatmap("Geelong Cats")
```

## Gold Coast Suns

```{r}
#| echo: false
create_uncontested_mark_heatmap("Gold Coast Suns")
```

## GWS Giants

```{r}
#| echo: false
create_uncontested_mark_heatmap("GWS Giants")
```

## Hawthorn

```{r}
#| echo: false
create_uncontested_mark_heatmap("Hawthorn")
```

## Melbourne

```{r}
#| echo: false
create_uncontested_mark_heatmap("Melbourne")
```

## North Melbourne

```{r}
#| echo: false
create_uncontested_mark_heatmap("North Melbourne")
```

## Port Adelaide

```{r}
#| echo: false
create_uncontested_mark_heatmap("Port Adelaide")
```

## Richmond

```{r}
#| echo: false
create_uncontested_mark_heatmap("Richmond")
```

## St Kilda

```{r}
#| echo: false
create_uncontested_mark_heatmap("St Kilda")
```

## Sydney Swans

```{r}
#| echo: false
create_uncontested_mark_heatmap("Sydney Swans")
```

## West Coast Eagles

```{r}
#| echo: false
create_uncontested_mark_heatmap("West Coast Eagles")
```

## Western Bulldogs

```{r}
#| echo: false
create_uncontested_mark_heatmap("Western Bulldogs")
```
:::

## Rebound 50s

##### (Player's Percentage of Rebound 50s for the Match)

::: panel-tabset
## Adelaide Crows

```{r}
#| echo: false
create_rebound_50_heatmap("Adelaide Crows")
```

## Brisbane Lions

```{r}
#| echo: false
create_rebound_50_heatmap("Brisbane Lions")
```

## Carlton

```{r}
#| echo: false
create_rebound_50_heatmap("Carlton")
```

## Collingwood

```{r}
#| echo: false
create_rebound_50_heatmap("Collingwood")
```

## Essendon

```{r}
#| echo: false
create_rebound_50_heatmap("Essendon")
```

## Fremantle

```{r}
#| echo: false
create_rebound_50_heatmap("Fremantle")
```

## Geelong Cats

```{r}
#| echo: false
create_rebound_50_heatmap("Geelong Cats")
```

## Gold Coast Suns

```{r}
#| echo: false
create_rebound_50_heatmap("Gold Coast Suns")
```

## GWS Giants

```{r}
#| echo: false
create_rebound_50_heatmap("GWS Giants")
```

## Hawthorn

```{r}
#| echo: false
create_rebound_50_heatmap("Hawthorn")
```

## Melbourne

```{r}
#| echo: false
create_rebound_50_heatmap("Melbourne")
```

## North Melbourne

```{r}
#| echo: false
create_rebound_50_heatmap("North Melbourne")
```

## Port Adelaide

```{r}
#| echo: false
create_rebound_50_heatmap("Port Adelaide")
```

## Richmond

```{r}
#| echo: false
create_rebound_50_heatmap("Richmond")
```

## St Kilda

```{r}
#| echo: false
create_rebound_50_heatmap("St Kilda")
```

## Sydney Swans

```{r}
#| echo: false
create_rebound_50_heatmap("Sydney Swans")
```

## West Coast Eagles

```{r}
#| echo: false
create_rebound_50_heatmap("West Coast Eagles")
```

## Western Bulldogs

```{r}
#| echo: false
create_rebound_50_heatmap("Western Bulldogs")
```
:::

## Goals

##### (Players Who Average More Than 0.5 Goals Per Game)

::: panel-tabset
## Adelaide Crows

```{r}
#| echo: false
create_goal_heatmap("Adelaide Crows")
```

## Brisbane Lions

```{r}
#| echo: false
create_goal_heatmap("Brisbane Lions")
```

## Carlton

```{r}
#| echo: false
create_goal_heatmap("Carlton")
```

## Collingwood

```{r}
#| echo: false
create_goal_heatmap("Collingwood")
```

## Essendon

```{r}
#| echo: false
create_goal_heatmap("Essendon")
```

## Fremantle

```{r}
#| echo: false
create_goal_heatmap("Fremantle")
```

## Geelong Cats

```{r}
#| echo: false
create_goal_heatmap("Geelong Cats")
```

## Gold Coast Suns

```{r}
#| echo: false
create_goal_heatmap("Gold Coast Suns")
```

## GWS Giants

```{r}
#| echo: false
create_goal_heatmap("GWS Giants")
```

## Hawthorn

```{r}
#| echo: false
create_goal_heatmap("Hawthorn")
```

## Melbourne

```{r}
#| echo: false
create_goal_heatmap("Melbourne")
```

## North Melbourne

```{r}
#| echo: false
create_goal_heatmap("North Melbourne")
```

## Port Adelaide

```{r}
#| echo: false
create_goal_heatmap("Port Adelaide")
```

## Richmond

```{r}
#| echo: false
create_goal_heatmap("Richmond")
```

## St Kilda

```{r}
#| echo: false
create_goal_heatmap("St Kilda")
```

## Sydney Swans

```{r}
#| echo: false
create_goal_heatmap("Sydney Swans")
```

## West Coast Eagles

```{r}
#| echo: false
create_goal_heatmap("West Coast Eagles")
```

## Western Bulldogs

```{r}
#| echo: false
create_goal_heatmap("Western Bulldogs")
```
:::
